### 2022-07-27 main/chapter_2ljets.tex
autoformat and quick proofread

With this decision, post-fit results (such as the summary plot of
Figure~\ref{fig:2ljets_summary})
indeed show no significant deviation from data in SR-Low-a or SR-Low-b,
and this $\zjets$ sample comparison is the main reason why.
Internal reviewers were, however, confused as to why we mentioned a deficit in
SR-Low that did not appear in the results plots or tables.
Much to my ire, the paper editors therefore removed all mentions of an SR-Low
deficit from the paper.
Despite bring real and significant, this deficit was erased from public view,
and to my knowledge is only reported through inner details of
the HistFactory models shared in our HEPData archive~\cite{hepdata.116034}.

@@

\subsubsection{Alternative diboson}
\label{sec:2ljets_diboson_alt}
No alternative samples were available for comparison with our central diboson
samples, which are simulated with \sherpa~2.2.2 at NLO with up to six
electroweak vertices.
To my knowledge, this is simply a limitation from what \atlas\ has decided to
spend its resources on, and quite reasonably since full simulation is
computationally expensive.
We did, however, have access to the cheaper alternative of set of small,
truth-level samples, that were simulated with the same \sherpa\ setup but with
varied parameters to assess uncertainties in the modelling of parton showers.

@@

Unfortunately, a total failure of statistical precision means that no
meaningful result can be derived from these variations.
First our regions receive very few raw events in each variation,
for example $1$ sample in SR-$\llbb$, around a dozen in
each SR-High bin, and a maximum of $597$ in CR-VZ.
Second, those samples carry weights in almost-equal mixtures of $+1$ and $-1$,
so they further lose precision in cancellation between the positive and
negative halves.

Variations for these samples were assigned by a scheme that follows a
convention set by other parts of the $\twoljets$ electroweak analysis.
With given central, up, and down variations of the yield, it works as
follows.
\begin{enumerate}
\item If both up and down variations lie to the same side of central, then
the variation is half the difference from up and down.
\item Otherwise (opposite sides of central), the variation is half of the
maximum absolute difference between central and up or down.
\item Any variation, from the above two bullets, that is smaller than the
largest statistical uncertainty on any of the samples is increased to the size
of that statistical uncertainty.
\item Directions of variation preserved by maintaining their signs, and
each variation is coupled between bins with its own single parameter.
\end{enumerate}
Point 1 acts to mitigate large variations where the variations lie far from
the central sample,
and all remainders are dominated by the statistical uncertainty due to point 3.

@@

In these looser regions VR-sys-main and VR-sys-OffShell, each variation
reduces to around $10\%$ and remains dominated by the statistical uncertainty.
Although local effects could occur, this a reasonable indication that these
parameters should not much affect our signal regions.
We therefore apply the variations measured in VR-sys-main to all on-shell
regions,
and the variations measured in VR-sys-OffShell to off-shell regions,
with one parameter coupling all regions for each of
$Q_\textrm{cut}^\textrm{CKKW}$,
\texttt{CSS\_KIN}, and
$S_Q$.

@@

\subsection{Other background variations}
\label{sec:2ljets_other_background_variations}
Many variations were evaluated, but few of them significantly impact the
results or have interesting details, so they are not covered in detail in
this thesis.
This section briefly lists some of the remaining variations.

@@

\paragraph{Miscellanea}
\begin{itemize}
\item A $\pm30\%$ variation on $\zjets$ is assigned in CR-tt only to cover our
uncertainty from extrapolation over $b$-tagged
jets~\cite{atlas_twiki_susytheoretical}.
\item Variations for the the \sherpa\ parton shower parameters
$Q_\textrm{cut}^\textrm{CKKW}$ and
$S_Q$ are assigned for $\zjets$.
Unlike the alternative samples used for diboson as described in
Section~\ref{sec:2ljets_diboson_alt}, these are assigned as functions of the
jet kinematics in each event by a parametrized method that avoids expensive
alternative simulations~\cite{Anders:2125718, atlas_twiki_susytheoretical}.
\emph{Thanks to Jon~Long and Yumeng~Cao for collaboration in preparing these
variations}.
\end{itemize}

>>>>

With this decision, post-fit results (such as the summary plot of
Figure~\ref{fig:2ljets_summary})
indeed show no significant deviation from data in SR-Low-a or SR-Low-b,
and this $\zjets$ sample comparison is the main reason why.
Internal reviewers were, however, confused as to why we mentioned a deficit in
SR-Low that did not appear in the results plots or tables.
Much to my ire, the paper editors therefore removed all mentions of an SR-Low
deficit from the paper.
Despite bring real and significant, this deficit was erased from public view,
and to my knowledge, is only reported through inner details of
the HistFactory models shared in our HEPData archive~\cite{hepdata.116034}.

@@

\subsubsection{Alternative diboson}
\label{sec:2ljets_diboson_alt}
No alternative samples were available for comparison with our central diboson
samples, which are simulated with \sherpa~2.2.2 at NLO with up to six
electroweak vertices.
This limitation is simply a result of how \atlas\ has decided to allocate
its limited resources on, and quite reasonably so, since full simulation is
computationally expensive.
We did, however, have access to the cheaper alternative set of small,
truth-level samples, that were simulated with the same \sherpa\ setup but with
varied parameters to assess uncertainties in the modelling of parton showers.

@@

Unfortunately, a total failure of statistical precision means that no
meaningful result can be derived from these variations.
First, our regions receive very few raw events in each variation,
for example $1$ sample in SR-$\llbb$, around a dozen in
each SR-High bin, and a maximum of $597$ in CR-VZ.
Second, those samples carry weights in almost-equal mixtures of $+1$ and $-1$,
so they further lose precision in cancellation between the positive and
negative halves.

Variations for these samples were assigned by a scheme that follows a
convention set by other parts of the $\twoljets$ electroweak analysis.
With given central, up, and down variations of the yield, it works as
follows.
\begin{enumerate}
\item If both up and down variations lie to the same side of central, then
the variation is half the difference from up and down.
\item Otherwise, opposite sides of central, the variation is half of the
maximum absolute difference between central and up or down.
\item Any variation, from the above two bullets, that is smaller than the
largest statistical uncertainty on any of the samples is increased to the size
of that statistical uncertainty.
\item Directions of variation preserved by maintaining their signs, and
each variation is coupled between bins with its own single parameter.
\end{enumerate}
Point 1 acts to mitigate large variations where the variations lie far from
the central sample,
and all remainders are dominated by the statistical uncertainty due to point 3.

@@

In the looser regions VR-sys-main and VR-sys-OffShell, each variation
reduces to around $10\%$ and remains dominated by the statistical uncertainty.
Although local effects could occur, this is a reasonable indication that these
parameters should not much affect our signal regions.
We therefore apply the variations measured in VR-sys-main to all on-shell
regions,
and the variations measured in VR-sys-OffShell to off-shell regions,
with one parameter coupling all regions for each of
$Q_\textrm{cut}^\textrm{CKKW}$,
\texttt{CSS\_KIN}, and
$S_Q$.

@@

\subsection{Other background variations}
\label{sec:2ljets_other_background_variations}
Many variations were evaluated, but few of them significantly impact the
results or have interesting details, so they are not covered in detail in
this thesis.
This section briefly lists some remaining variations.

@@

\paragraph{Miscellanea}
\begin{itemize}
\item A $\pm30\%$ variation on $\zjets$ is assigned in CR-tt only to cover our
uncertainty from extrapolation over $b$-tagged
jets~\cite{atlas_twiki_susytheoretical}.
\item Variations for the \sherpa\ parton shower parameters
$Q_\textrm{cut}^\textrm{CKKW}$ and
$S_Q$ are assigned for $\zjets$.
Unlike the alternative samples used for diboson as described in
Section~\ref{sec:2ljets_diboson_alt}, these are assigned as functions of the
jet kinematics in each event by a parametrized method that avoids expensive
alternative simulations~\cite{Anders:2125718, atlas_twiki_susytheoretical}.
\emph{Thanks to Jon~Long and Yumeng~Cao for collaboration in preparing these
variations}.
\end{itemize}
